00-OD-preparation

### 2022-04-14 00-OD-preparation.Rmd
added column to identify which zone is a LEZ in 00-data-prep

zn <- st_read("data-raw/zn.shp")
```
Importing the spatial object which corresponds to the low-emission-zones
```{r}
#XXX
```

>>>>

zn <- st_read("data-raw/zn.shp")
```
Importing the spatial object which corresponds to the low-emission-zones
```{r}
zn_LEZ <- st_read("data-raw/LEZ.shp") %>% transmute(ZT1259, 
                                                                       LEZ = 1)
```

Add a column which indicates if a zn is within the center of madrid:
```{r}
zn <- zn %>% merge(zn_city %>% st_drop_geometry(), by = c("ZT1259"), all.x=TRUE)
```

plot and color in madrid city:
```{r}
#plot to double check that centroids are on zones
ggplot() +
  geom_sf(data = zn, aes(fill = as.factor(city)), col = NA) +
  scale_fill_manual(values = c("red", "grey"), name= "Cluster Group")
```
```{r}
#plot to double check that centroids are on zones
ggplot() +
  geom_sf(data = zn_city,) 
```
